Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-03 analysis/sim/run_simpw.Rmd
fig

---
title: "Examining background gene lists using simulation - comparison of different enrichment techniques"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
theme: cosmo
---

@@

@@

```{r,rqesults}

@@

cp <- subset(res,PWAY_FUNC == "clusterprofiler")
fo <- subset(res,PWAY_FUNC == "fora")
fg <- subset(res,PWAY_FUNC == "fgsea")
mi <- subset(res,PWAY_FUNC == "mitch")

>>>>

---
title: "Examining background gene lists using simulation - comparison of different enrichment techniques"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

saveRDS(res,file="res.Rds")

@@

```{r,results}

@@

cp <- subset(res,PWAY_FUNC == "clusterprofiler")
fo <- subset(res,PWAY_FUNC == "fora")
fg <- subset(res,PWAY_FUNC == "fgsea")

cp %>% kbl(caption="clusterprofiler") %>% kable_paper("hover", full_width = F)
fo %>% kbl(caption="fora") %>% kable_paper("hover", full_width = F)
fg %>% kbl(caption="fg") %>% kable_paper("hover", full_width = F)
